# Data transformation

Based on data copied from data sources, we can read it into our project with R function read.csv(). We first read team statistics and rename the team abbreviation. Samples below:
```{r}
team_stats = read.csv("./data/team_stats.csv")
team_stats_new = team_stats
team_stats_new$Name=c("100T","C9","DFM","DK","EDG","FNC","FPX","GENG","HLE","LNG","MAD","PSG","RGE","RNG","T1","TL")
team_stats_new$Name
```

Then we merge teams' rank into team stats. Samples below:

```{r}
# add rank of each time
rank = c(1,2,4,4,8,8,8,8,16,16,16,16,16,16,16,16)
Name = c("EDG","DK","GENG","T1","RNG","C9","HLE","MAD","RGE","FPX","100T","DFM","PSG","FNC","LNG","TL")
rank.dat = data.frame(Name,rank)

# merge rank to team stats
team_stats_comp= merge(team_stats_new,rank.dat,by="Name")
team_stats_comp %>% select(Name, rank)
```

When data was read into R, some data type are all characters. Therefore, we converted data type to the correct one. For better analysis, we transformed variable “Game.Duration” from character to numeric format. Besides, some data ends with % notation. So we removed %, converted it into numeric value. Additionally, there is one column called Region and one value of it is NA, which stands for North America. However, R will count it as unavailable values. Therefore, we transformed this kind of value to NA(North America). Here are samples of our transformed data:

```{r}
library(dplyr)
team_stats_comp[is.na(team_stats_comp)] = "NA"
team_stats_comp = team_stats_comp %>%
  select(-Season)
for(i in 1:nrow(team_stats_comp)){
  time = str_split(team_stats_comp[i,8], ":")[[1]]
  team_stats_comp[i,8] = round((as.numeric(time[1])+as.numeric(time[2])/60), digits = 2)
}
team_stats_comp$Win.rate = as.numeric(gsub("[\\%,]","",team_stats_comp$Win.rate))/100
team_stats_comp %>% select(Name, Region, Game.duration)
```
Then we read players' data into our project but our data does not bind players to their belonging teams. So we add that to our players' data. We delete pentakill rates and solo kill rates. Other players' data transformations are almost the same as the transformations of teams' data. Here are samples of our transformed data:

```{r}
library(stringr)
# player_stats
# add each play belongs to which team
top_stats = read.csv("./data/top_stats.csv")
top_team = read.csv("./data//top_team.csv")
top_stats$Player = str_trim(top_stats$Player,side="right")
top_stats$Player = str_to_title(top_stats$Player) 
top_team$Player = str_trim(top_stats$Player,side="right")
top_team$Player = str_to_title(top_stats$Player) 
top_stats_comp = merge(top_stats,top_team,by="Player")
top_stats_comp = top_stats_comp %>% select(-c(Penta.Kills, Solo.Kills))
top_stats_comp$Win.rate = as.numeric(gsub("[\\%,]","",top_stats_comp$Win.rate))/100
top_stats_comp$KP. = as.numeric(gsub("[\\%,]","",top_stats_comp$KP.))/100
top_stats_comp$FB.Victim = as.numeric(gsub("[\\%,]","",top_stats_comp$FB.Victim))/100
top_stats_comp$FB.. = as.numeric(gsub("[\\%,]","",top_stats_comp$FB..))/100

jug_stats = read.csv("./data//jug_stats.csv")
jug_team = read.csv("./data//jug_team.csv")
jug_stats$Player = str_trim(jug_stats$Player,side="right")
jug_stats$Player = str_to_title(jug_stats$Player) 
jug_team$Player = str_trim(jug_stats$Player,side="right")
jug_team$Player = str_to_title(jug_stats$Player) 
jug_stats_comp = merge(jug_stats,jug_team,by="Player")
jug_stats_comp = jug_stats_comp %>% select(-c(Penta.Kills, Solo.Kills))
jug_stats_comp$Win.rate = as.numeric(gsub("[\\%,]","",jug_stats_comp$Win.rate))/100
jug_stats_comp$KP. = as.numeric(gsub("[\\%,]","",jug_stats_comp$KP.))/100
jug_stats_comp$FB.Victim = as.numeric(gsub("[\\%,]","",jug_stats_comp$FB.Victim))/100
jug_stats_comp$FB.. = as.numeric(gsub("[\\%,]","",jug_stats_comp$FB..))/100

mid_stats = read.csv("./data//mid_stats.csv")
mid_team = read.csv("./data//mid_team.csv")
mid_stats$Player = str_trim(mid_stats$Player,side="right")
mid_stats$Player = str_to_title(mid_stats$Player) 
mid_team$Player = str_trim(mid_stats$Player,side="right")
mid_team$Player = str_to_title(mid_stats$Player) 
mid_stats_comp = merge(mid_stats,mid_team,by="Player")
mid_stats_comp = mid_stats_comp %>% select(-c(Penta.Kills, Solo.Kills))
mid_stats_comp$Win.rate = as.numeric(gsub("[\\%,]","",mid_stats_comp$Win.rate))/100
mid_stats_comp$KP. = as.numeric(gsub("[\\%,]","",mid_stats_comp$KP.))/100
mid_stats_comp$FB.Victim = as.numeric(gsub("[\\%,]","",mid_stats_comp$FB.Victim))/100
mid_stats_comp$FB.. = as.numeric(gsub("[\\%,]","",mid_stats_comp$FB..))/100

bot_stats = read.csv("./data//bot_stats.csv")
bot_team = read.csv("./data//bot_team.csv")
bot_stats$Player = str_trim(bot_stats$Player,side="right")
bot_stats$Player = str_to_title(bot_stats$Player) 
bot_team$Player = str_trim(bot_stats$Player,side="right")
bot_team$Player = str_to_title(bot_stats$Player) 
bot_stats_comp = merge(bot_stats,bot_team,by="Player")
bot_stats_comp = bot_stats_comp %>% select(-c(Penta.Kills, Solo.Kills))
bot_stats_comp$Win.rate = as.numeric(gsub("[\\%,]","",bot_stats_comp$Win.rate))/100
bot_stats_comp$KP. = as.numeric(gsub("[\\%,]","",bot_stats_comp$KP.))/100
bot_stats_comp$FB.Victim = as.numeric(gsub("[\\%,]","",bot_stats_comp$FB.Victim))/100
bot_stats_comp$FB.. = as.numeric(gsub("[\\%,]","",bot_stats_comp$FB..))/100

sup_stats = read.csv("./data//sup_stats.csv")
sup_team = read.csv("./data//sup_team.csv")
sup_stats$Player = str_trim(sup_stats$Player,side="right")
sup_stats$Player = str_to_title(sup_stats$Player) 
sup_team$Player = str_trim(sup_stats$Player,side="right")
sup_team$Player = str_to_title(sup_stats$Player) 
sup_stats_comp = merge(sup_stats,sup_team,by="Player")
sup_stats_comp = sup_stats_comp %>% select(-c(Penta.Kills, Solo.Kills))
sup_stats_comp$Win.rate = as.numeric(gsub("[\\%,]","",sup_stats_comp$Win.rate))/100
sup_stats_comp$KP. = as.numeric(gsub("[\\%,]","",sup_stats_comp$KP.))/100
sup_stats_comp$FB.Victim = as.numeric(gsub("[\\%,]","",sup_stats_comp$FB.Victim))/100
sup_stats_comp$FB.. = as.numeric(gsub("[\\%,]","",sup_stats_comp$FB..))/100

top_stats_comp %>% select(Player, Team, Win.rate)
```


